Adopting agile software development in the large organizations: A systematic literature review

### 2014-05-21 journal/article.tex
S:  Having a positive experience

It is clear that any positive results will facilitate an organizational
transformation. Although a recipie to fabricate positive experiences can not be
given, many cases described how they had succeeded. Benefield [P6] describes how
a survey was done to objectively measure satisfaction in agile, and the positive
results helped teams make the decision to change their way of working. Another
case describes how the corporate agile awareness and teaching event was designed
to be fun and engaging, which made people take more ethusiasm in applying the
agile practices [P32]. The move towards agile is assisted by making any benefits
publicly visible and celebrating even the small victories [P40, P42].

>>>>

It is clear that any positive results will facilitate an organizational
transformation. Although a recipie to fabricate positive experiences can not be
given, many cases described how they had succeeded. Benefield [P6] describes how
a survey was done to objectively measure satisfaction in agile, and the positive
results helped teams make the decision to change their way of working. Benefield
describes further how management was requesting proof on better performance as a
response to requests to increase coaching and training budget. After conducting
inquiries the coaching team was able to present an estimate of a 30\% increase
in performance, which made management highly convinced [P6]. Another case
describes how the corporate agile awareness and teaching event was designed to
be fun and engaging, which made people take more ethusiasm in applying the agile
practices [P32]. The move towards agile is assisted by making any benefits
publicly visible and celebrating even the small victories [P40, P42].
